Endogenous Heterogeneous Innovation

### 2018-03-07 Presentations/Proposal/SE-Presentation.tex
Added GMM
Fixed the histogram

\begin{frame}{Theory Outline}
	\begin{itemize}\itemsep12pt
	\item Akcigit and Kerr (2016) included two different types of innovation (incremental and abrupt). Firms had no control over what type of innovation their R\&D efforts would result in.
	\item We want to endogenize this distinction. Firms choose how much to invest in abrupt or internal innovations.
	\item We attempt to fit this model to patent citation distributions. The fit gives an impression of how well the model reflects reality. Also, the resulting parameter values have important theoretical interpretations.
	\end{itemize}
\end{frame}

@@

%The graphics in this slide need to be updated. I want it to have the histogram of abrupt patent citations that we are fitting the model to.
\begin{frame}{Data - Patent Citation Distributions}
	\begin{center}
	\begin{figure}\centering\label{Innov7}
	\begin{minipage}[b]{0.45\linewidth}
	  \fbox{\resizebox{2.0in}{1.8in}{\includegraphics{Patent_citation_distr.png}}}
	\end{minipage}
	\begin{minipage}[b]{0.45\linewidth}
		\fbox{\resizebox{2.0in}{1.8in}{\includegraphics{Patent_citation_distr_cut.png}}}
	\end{minipage}
	\end{figure}
	\end{center}
	Summary: \# obs = 3,278,174; Mean = 11.76; Std. Dev. = 20.00
\end{frame}

@@

\begin{frame} {Estimation Results}
	\begin{itemize}\itemsep 12pt
		\item $\alpha = 1$, $\lambda_{int, 0}= 0.357 $, $(\lambda_{abr} + \tau = 0.355 $\\
		\begin{center}
		\begin{figure}\centering\label{Innov5}
		  \fbox{\resizebox{3.2in}{2.2in}{\includegraphics{MLE.png}}}
		\end{figure}
		\end{center}
%Comment on how the alpha estimate implies constant step size. Talk about missing the mass at zero citations.
	\end{itemize}
\end{frame}

@@

\begin{frame} {Robustness}
	\begin{itemize}\itemsep 12pt
		\item Untargeted moment: share of incremental R\&D over total:
		\begin{table}
		\centering
		\begin{tabular}{l llp{1.5cm} p{0.5cm} llp{1.5cm}}
		\toprule
		Moment & \multicolumn{1}{c}{Data} & \multicolumn{1}{c}				{Model} \\ 
		\midrule
		Incremental/total & 0.90 & 0.78\\
		\bottomrule
		\end{tabular}
		\end{table}
	\end{itemize}
\end{frame}

>>>>

\begin{frame}{Theory Outline}
	\begin{itemize}\itemsep12pt
	\item Akcigit and Kerr (2016) included two different types of innovation (incremental and external abrupt). Firms can't do internal abrupt innovation (ex: no internal new product generation) and internal R\&D has no diminishing returns.
	\item We want to endogenize those features. Firms choose how much to invest in internal abrupt or incremental innovations.
	\item We attempt to fit this model to patent citation distributions. The fit gives an impression of how well the model reflects reality. Also, the resulting parameter values have important theoretical interpretations.
	\end{itemize}
\end{frame}

@@

%The graphics in this slide need to be updated. I want it to have the histogram of abrupt patent citations that we are fitting the model to.
\begin{frame}{Data - Patent Citation Distributions}
	\begin{center}
	\begin{figure}\centering\label{Innov7}
	\begin{minipage}[b]{0.45\linewidth}
	  \fbox{\resizebox{2.0in}{1.8in}{\includegraphics{SameClass_hist.png}}}
	\end{minipage}
	\begin{minipage}[b]{0.45\linewidth}
		\fbox{\resizebox{2.0in}{1.8in}{\includegraphics{SameClass_hist_ex0.png}}}
	\end{minipage}
	\end{figure}
	\end{center}
	Summary: \# obs = 189,207; Mean = 10.06; Std. Dev. = 18.43
\end{frame}

@@

\begin{frame} {Estimation Results}
	\begin{itemize}\itemsep 12pt
		\item $\alpha = 1$, $\lambda_{int, 0}= 0.357 $, $\lambda_{abr} + \tau = 0.0355 $\\
		\begin{center}
		\begin{figure}\centering\label{Innov5}
		  \fbox{\resizebox{3.2in}{2.2in}{\includegraphics{MLE.png}}}
		\end{figure}
		\end{center}
%Comment on how the alpha estimate implies constant step size. Talk about missing the mass at zero citations.
	\end{itemize}
\end{frame}

@@

\begin{frame} {Robustness}
	\begin{itemize}\itemsep 6pt
		\item We ran a GMM estimation: $\alpha = 1$, $\lambda_{int, 0}= 0.351 $, $\lambda_{abr} + \tau = 0.047 $
		\begin{center}
		\begin{figure}\centering\label{Innov5}
		  \fbox{\resizebox{2.9in}{2.3in}{\includegraphics{GMM_MLE.png}}}
		\end{figure}
		\end{center}
	\end{itemize}
\end{frame}

\begin{frame} {Robustness - GMM}
	\begin{itemize}\itemsep 12pt
		\item Moments (GMM):
		\begin{table}
		\centering
		\begin{tabular}{l llp{1.5cm} p{0.5cm} llp{1.5cm}}
		\toprule
		Moment & \multicolumn{1}{c}{Data} & \multicolumn{1}{c}				{Model} \\ 
		\midrule
		Mean of citations & 10.06 & 7.39\\
		Mean of first 5 seq. ratios & 0.57 & 0.88\\
		Sum of first 2 bins & 0.26 & 0.22\\
		R\&D Intensity & 0.068 & 0.068\\
		Criterion & & 0.386\\
		\bottomrule
		\end{tabular}
		\end{table}\vspace{-0.2cm}
		\item Untargeted moment: share of incremental R\&D over total:
		\begin{table}
		\centering
		\begin{tabular}{l llp{1.5cm} p{0.5cm} llp{1.5cm}}
		\toprule
		Moment & \multicolumn{1}{c}{Data} & \multicolumn{1}{c}				{Model} \\ 
		\midrule
		MLE\\
		\;Incremental/total & .90 & .78\\
		GMM\\
		\;Incremental/total & .90 & .88\\
		\bottomrule
		\end{tabular}
		\end{table}
	\end{itemize}
\end{frame}
